Exploring Nonlinear Atmospheric Influences on Temperature Using Polynomial Regression at Vancouver International Airport

### 2024-11-30 paper/paper.qmd
round table to 2 decimals

# Calculate VIF
vif_values <- vif(glm)
kable(vif_values)
```

@@

results <- data.frame(
  Metric = c("SSR", "TSS", "R2", "R2-Train", "MSE-Train", "MSE-Test"),
  Value = c(SSR, TSS, R2, R2T, mse_train, mse_test)
)

@@

>>>>

# Calculate VIF
vif_values <- round(vif(glm), 2)
kable(vif_values)
```

@@

results <- data.frame(
  Metric = c("SSR", "TSS", "R2", "R2-Train", "MSE-Train", "MSE-Test"),
  Value = c(SSR, TSS, R2, R2T, mse_train, mse_test)
)
results$Value <- round(results$Value, 2)

@@

metrics <- metrics %>%
  mutate(RMSE = round(RMSE, 2), MAE = round(MAE, 2))
